---
title: "Dey_Review.Rmd"
author: "Sristi Dey"
date: "2025-03-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hi Viraaj, 

I found an error in loading library(reshape2) and library(naniar) while running your markdown file, "Error in library(reshape2) : there is no package called ‘reshape2’". 
I removed them to be able to run your markdown file further, got an error in line 292 "could not find function (replace_with_na)"

Your Single Nucleotide Polymorphism per Chromosome plot looks good, however, it does not have the information for 'multiple' and 'unknown'

#Plot Single Nucleotide Polymorphism per Sample
For this plot it would be better to read the chromosomes in order in the x-axis, below code can help you order them from 1-10, then the non-numeric chromosomes
```{r sort  using factor}
your merged maize data$Chromosome <- factor(your merged maize data$Chromosome, 
    levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "multiple", "unknown"))
```

Due to the error in line 292 i could not generate your missing information plots. Overall, everything else look good. 

